---
title: "Module 2 - Assignment 2"
author: "Stockton, Skylar"
output: word_document
---

```{r}
# install all necessary libraries if not installed at once like so
# install.packages(c("tidyverse", "tidymodels", "glmnet", "GGally", "ggcorrplot", "MASS", "car", "lubridate", "lmtest", "splines"))

# load libraries
library(tidyverse)
library(tidymodels)
library(glmnet)
library(GGally)
library(corrplot)
library(MASS)
library(car)
library(lubridate)
library(lmtest)
library(splines)

# load data
bike <- read.csv("bike_cleaned.csv") # adjust as necessary

# Mutations
bike = bike %>% mutate(dteday = mdy(dteday))
bike = bike %>% mutate_if(is.character, as_factor)
bike = bike %>% mutate(hr = as_factor(hr))
```

Question 1:
```{r}
corr_data <- bike[, sapply(bike, is.numeric)] %>% dplyr::select(-c(instant,casual,registered)) # removing columns
corrplot(cor(corr_data), type = "upper", method = "number", order = "alphabet", 
         tl.col = "black")
```
Answer: Variable with the highest absolute correlation to "count".

Question 2:
```{r}
ggplot(bike, aes(x=factor(season), y=count)) + geom_boxplot()
```
Answer: Season with the highest median in box plot.

Question 3:
```{r}
lm_hr <- linear_reg() %>% 
    set_engine("lm") %>% 
    fit(count ~ hr, data = bike)
summary(lm_hr$fit)
```
Answer: (24 levels of hour -1) = 23 Dummy variables 

Question 4:
Answer: The one without a coefficient.

Question 5:
```{r}
min_hr <- summary(lm_hr$fit)$coefficients[which.min(summary(lm_hr$fit)$coefficients[,1]),]
names(min_hr)
```
Answer: Hour with the lowest coefficient value.

Question 6:
```{r}
ggplot(bike, aes(x=temp, y=count)) + geom_point()
```
Answer: The graphical output should give you a hint.

Question 7:
```{r}
lm_hr_temp <- linear_reg() %>% 
    set_engine("lm") %>% 
    fit(count ~ hr + temp, data = bike)
summary(lm_hr_temp$fit)$coefficients
```
Answer: Value of the coefficient for "hr23".

Question 8:
```{r}
summary(lm_hr_temp$fit)$adj.r.squared
```
Answer: R-squared adjusted value.

Question 9:
```{r}
lm_temp_atemp <- linear_reg() %>% 
    set_engine("lm") %>% 
    fit(count ~ temp + atemp, data = bike)
summary(lm_temp_atemp$fit)$coefficients
summary(lm_temp_atemp$fit)$adj.r.squared
```
Answer: R-squared adjusted value.

Question 10:
Answer: Those with p-value < 0.05 are significant.

Question 11:
Answer: C. Multicollinearity

Question 12:
```{r}
allmod <- lm(count ~ season + mnth + hr + holiday + weekday + workingday + weathersit + temp + atemp + hum + windspeed, data = bike)
summary(allmod)
```
Answer: B. weekday and holiday

Question 13:
```{r}
# backward stepwise regression
library(MASS)
step <- stepAIC(allmod, direction = "backward")
summary(step)
```
Answer: Variable with the highest p-value which is also above 0.05. This will depend on the results of your analysis.