---
title: "Module 2 - Assignment 1"
author: "Stockton, Skylar"
output: word_document
---

Since I can't actually run R code in here, below is the code you would use for each question and a description of how to answer each:

```{r}
library(tidyverse)
library(tidymodels)
library(GGally)
library(lmtest)

air = airquality
```

Question 1: 
```{r}
nrow(air)
```
Answer: Number of rows in the console output.

Question 2: 
```{r}
ncol(air)
```
Answer: Number of columns in the console output.

Question 3: 
```{r}
any(is.na(air$Ozone)) # True if yes, False if no
```

Question 4: This would depend on the context of the study/question but generally, one might choose "Ozone" because it's a factor that is often studied in terms of its relationship with other atmospheric qualities. 

```{r}
air2 = air %>% drop_na()
```

Question 5: 
```{r}
nrow(air2)
```
Answer: Number of rows in the console output.

Question 6: 
```{r}
ncol(air2)
```
Answer: Number of columns in the console output.

Question 7: 
```{r}
ggpairs(air2) 
ggcorr(air2,label = TRUE)
```

Answer: The variable with the highest absolute correlation to "Ozone".

Question 8:

Answer: The variable with the lowest absolute correlation to "Ozone".

Question 9: 
```{r}
ggplot(air2) + geom_point(aes(x = Temp, y = Ozone))
```
Answer: The graphical output should give you a hint about the nature of the relationship.

Question 10:
```{r}
lmFit <- linear_reg() %>% 
    set_engine("lm") %>% 
    fit(Ozone ~ Temp, data = air2)

lmFit$fit$coefficients["Temp"]
```
Answer: The value of the slope coefficient in the output.

Question 11:
```{r}
summary(lmFit$fit)$r.squared
```
Answer: R-squared value in the output.

Question 12: You would check the p-value for the Temp variable in the model.
```{r}
summary(lmFit$fit)$coefficients["Temp", "Pr(>|t|)"] < 0.05
```
If result is TRUE, then Temp is statistically significant.

Question 13:
```{r}
confint(lmFit$fit)
```
If the lower and upper bounds for Temp do not contain zero, then it's TRUE otherwise FALSE.

Question 14:
```{r}
predict(lmFit, new_data = data.frame(Temp = 80))
```
Answer: Extraction of the predicted "Ozone" value.

Question 15:

Code: Generate residuals plots to review the assumptions of linear regression (e.g., normality of errors, equal variance, independence of errors). 

```{r}
plot(lmFit$fit$residuals ~ air2$Temp)
abline(h = 0, col = "red") #for zero line
hist(lmFit$fit$residuals)
qqnorm(lmFit$fit$residuals)
qqline(lmFit$fit$residuals)
```

Answer: Graphical review of model assumptions for any obvious violations.